prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-06-07 inst/MyArticle/paper.Rmd
set R code snippet width=70

```{r setup, include=FALSE}
## See ACS guidelines [https://publish.acs.org/publish/author_guidelines?coden=ancham#manuscript_text_components]
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 7,
                      fig.height = 5)
```

@@

\newpage
## Miscellaneous {.unlisted .unnumbered}

>>>>

```{r setup, include=FALSE}
## See ACS guidelines [https://publish.acs.org/publish/author_guidelines?coden=ancham#manuscript_text_components]
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 7,
                      fig.height = 5)

options(width=70)
```

@@

## Miscellaneous {.unlisted .unnumbered}
